Creating the ``r params$package_name`` R package

### 2025-10-07 create-FSHybridPLS.Rmd
delete test

@@

```{r}
curve_normalize_train_test <- function(train, test){
  train_normalized <- train
  test_normalized <- test
  deno_train <- rep(NA, train@n_functional)
  for (k in 1:train@n_functional){ # for kth functional predictor
    mean_train <- mean.fd(train@functional_list[[k]]) # train mean function
    centered_train <- center.fd(train@functional_list[[k]])
    sd_train <- sd.fd(train@functional_list[[k]])
    deno_train[k] <- sqrt(inprod(sd_train, sd_train))

    train_normalized@functional_list[[k]] <- curve_normalize(
      train_normalized@functional_list[[k]],
      mean_train,
      deno_train[k]
      )

    test_normalized@functional_list[[k]] <-
      curve_normalize(
        test_normalized@functional_list[[k]],
        mean_train,
        deno_train[k]
      )
  }
  return( list(
    train = train_normalized,
    test = test_normalized,
    deno_train = deno_train
    ))}
```

>>>>

```{r}
#' 
#' @export
curve_normalize <- function(functional, mean_functional, deno){
  # operation also takes care of the original_X

  functional_normalized <- fd(coef =
                                coef(functional) - coef(mean_functional) %*% matrix(1, ncol = ncol(coef(functional))),
                              basisobj = functional$basis
                              )#numerator
  functional_normalized <- times.fd(1/deno, functional_normalized)
  return(functional_normalized)
}
```

@@
